%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{Guo Yu - Page \thepage\ of 2}%
\rfoot{}
\renewcommand{\headrulewidth}{0pt}%
\renewcommand{\footrulewidth}{0pt}%

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large{GUO, Yu} ~ \small{update: 06/06/2016}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    3019 Donald Bren Hall             \hfill +1(424)325-8267  \\
    Computer Science Dept.                      \hfill \href{mailto:guo.yu@uci.edu}{guo.yu@uci.edu}  \\
    University of California, Irvine                   \hfill \href{mailto:tflsguoyu@gmail.com}{tflsguoyu@gmail.com}\\
    Irvine, CA 92697-3435               \hfill \href{https://tflsguoyu.github.io}{https://tflsguoyu.github.io} \\
    
    %__________________________________________________________________________________________________________________
    % Research Interests
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Current\\Position}

    \textbf{University of California, Irvine (\href{http://www.uci.edu/}{UCI})}       \hfill \textbf{Irvine, CA, US}  \\
    \textsl{Ph.D Student in Computer Science} 															\hfill \textbf{Sept. 2016 -- present} \\
    Advisor: \href{https://shuangz.com/}{ZHAO Shuang} \\
    Interests: Computer Graphics \\

    % \textbf{Institute for Media Innovation (\href{http://imi.ntu.edu.sg/Pages/Home.aspx}{IMI}) @ \href{http://www.ntu.edu.sg/Pages/home.aspx}{NTU}}       \hfill \textbf{Singapore}  \\
    % \textsl{Research Associate} \\
    % Supervisor: \href{http://www.ntu.edu.sg/home/astjcham/}{Prof. Cham Tat-Jen} \textsl{(NTU)}  \\
    % Collaborators: \href{https://graphics.ethz.ch/~plaffont/}{Dr. Pierre-Yves Laffont}\textsl{(ETH Z\"{u}rich)},
    % \href{https://graphics.ethz.ch/~martint/}{Dr. Tobias Martin} \textsl{(ETH Z\"{u}rich)} \\
    % Interests: Computer Graphics, Computer Vision, GPGPU \\

    %__________________________________________________________________________________________________________________
    % Education
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Education}

    \textbf{University of Chinese Academy of Sciences (\href{http://english.ucas.ac.cn/Pages/default.aspx}{UCAS})}  \hfill \textbf{Beijing \& Shenzhen, China}\\
    \textsl{M.S. in Computer Science}                 \hfill \textbf{Sept. 2010 -- Jul. 2013} \\
	Thesis: GPU-based Soft Body Deformation with Nonlinear Finite Element Method. \\
	Advisor: \href{http://www.cse.cuhk.edu.hk/~pheng/}{HENG Pheng-Ann} (\href{http://www.cuhk.edu.hk/english/index.html}{CUHK})\\
	Major courses: Combinatorial Mathematics; Matrix Analysis; Stochastic Process; Computer Aided Geometric Design; Computer Graphics; Computer Vision; Visualization.

    \textbf{Central South University (\href{http://iecd.csu.edu.cn/en-US/Default.aspx}{CSU})}      \hfill \textbf{Changsha, China} \\
    \textsl{B.S. in Mathematics and Applied Mathematics}                \hfill \textbf{Sept. 2006 -- Jul. 2010}  \\
	Thesis: Forces Distribution with Fractal Theory in High Velocity Compaction Technology. \\
    Major courses: Mathematical Analysis; Linear Algebra; Spatial and Analytical Geometry; Real Analysis \& Functional Analysis; Modern Algebra; Topology; Partial Differential Equation; Optimal Theory. \\
    
    %__________________________________________________________________________________________________________________
    % Publications
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Publications}

    Derric Eng, Belle Yick, \textbf{Yu Guo}, Hong Xu, Miriam Reiner, Tat-Jen Cham, Annabel Chen.
    ``\textbf{Holistic and featural processing for 2D and 3D face recognition}".
    \textsl{The 11th Asia-Pacific Conference on Vision (APCV 2015)}, Singapore, July 10-12, 2015\\

    \vspace{-5mm}

    Ping Liu, Lin Shi, Defeng Wang, \textbf{Yu Guo}, Jianying Li, Jing Qin, Pheng-Ann Heng.
    ``\textbf{GPU Accelerated CBCT Reconstruction from Few Views with SART and TV Regularization}".
    \textsl{The Sixth International Workshop on High Performance Computing for Biomedical Image Analysis (HPC-MICCAI 2013)}, Nagoya, Japan, Sep.22-26, 2013\\

    \vspace{-5mm}

    Jiang Guo, Jun Cheng, Jianxin Pang, \textbf{Yu Guo}.
    ``\textbf{Real-time Hand Detection Based on Multi-stage HOG-SVM Classifier}".
    \textsl{2013 IEEE International Conference on Image Processing (ICIP 2013)}, Melbourne, Australia, Sep.15-18, 2013\\

    \vspace{-5mm}

    \textbf{Yu Guo}, Jianying Li, Ping Liu, Qiong Wang, Jing Qin.
    ``\textbf{A GPU-Accelerated Finite Element Solver for Simulation of Soft-Body Deformation}".
    \textsl{2013 IEEE International Conference on Information and Automation (ICIA 2013)}, Yinchuan, China, Aug.26-28, 2013\\

    \vspace{-5mm}

    \textbf{Yu Guo}, Jing Qin.
    ``\textbf{A Survey on Simulation of Soft Tissue Deformation in Virtual Surgery}"(In Chinese).
    \textsl{Journal of Integration Technology}, 2013\\

    \vspace{-5mm}

    \textbf{Yu Guo}.
    ``\textbf{Fall over or Sliding down?}"
    \textsl{ACM SIGGRAPH Asia 2012, Poster}, Singapore, Nov.28-Dec.1, 2012\\

    \vspace{-5mm}

    Jianying Li, \textbf{Yu Guo}, Heye Zhang, Yongming Xie.
    ``\textbf{A Master-Slave Robotic Simulator Based on GPUDirect}".
    \textsl{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2012)}, Vilamoura, Algarve, Portugal, Oct.7-12, 2012\\


    %________________________________________________________________________________________________________________
    % Professional Experience
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Research\\ Experiences}

    \textbf{Nanyang Technological University (\href{http://www.ntu.edu.sg/Pages/home.aspx}{NTU})}
    \hfill \textbf{Singapore} \\
    \textsl{Research Associate at Institute for Media Innovation (\href{http://imi.ntu.edu.sg/Pages/Home.aspx}{IMI})} \\

    % \vspace{-3mm}

    \begin{list2}

	\item \textsl{Project in BeingThere Centre, (\href{http://imi.ntu.edu.sg/BeingThereCentre/Pages/BTChome.aspx}{BTC-NTU} \& \href{http://beingthere.ethz.ch/}{BTC-ETH})}  \hfill \textbf{June 2014 -- Mar. 2016}  \\
   	Major works: 	\\
   	   	% Flow estimation of image pairs (Optical Flow/Sift Flow);
        % Face tracking and reconstruction by Kinect and Faceshift;
    Collaborators: 	\href{https://graphics.ethz.ch/~martint/}{Tobias MARTIN} \textsl{(ETH Z\"{u}rich)},
                   	\href{http://cs.brown.edu/~pylaffont/}{Pierre-Yves LAFFONT} \textsl{(ETH Z\"{u}rich)}
    \\
    \item \textsl{Project in BeingThere Centre, (\href{http://imi.ntu.edu.sg/BeingThereCentre/Pages/BTChome.aspx}{BTC-NTU} \& \href{http://beingthere.ethz.ch/}{BTC-ETH})}  \hfill  \textbf{Oct. 2013 -- May 2014}  \\
    Major works: 	Physical-based video manipulating;
            		Video segmentation (foreground subtraction);
            		Multi-view 3D reconstruction (structure from motion);
            		3D pose estimation.\\
    Collaborators: 	\href{https://graphics.ethz.ch/~jebazin/}{Jean-Charles BAZIN} \textsl{(Disney Z\"{u}rich)},
                   	\href{https://graphics.ethz.ch/~martint/}{Tobias MARTIN} \textsl{(ETH Z\"{u}rich)},
                   	\href{https://graphics.ethz.ch/~ckuster/}{Claudia PL\"{U}SS} \textsl{(ETH Z\"{u}rich)}
    \\
    \item \textsl{Project in BeingThere Centre, (\href{http://imi.ntu.edu.sg/BeingThereCentre/Pages/BTChome.aspx}{BTC-NTU} \& \href{http://www.hss.ntu.edu.sg/Pages/Home.aspx}{HSS-NTU})}  \hfill  \textbf{Dec. 2013 -- Dec. 2014}  \\
    Major works: 	2D and stereo face rendering. \\
    Collaborators: 	\href{http://edu.technion.ac.il/haptech/group/miriam_home.html}{Miriam REINER} \textsl{(Technion)},
                   	\href{http://www.hss.ntu.edu.sg/Programmes/psychology/people/Pages/BelleYick.aspx}{Belle Yee Ying YICK} \textsl{(NTU)}
    
    \end{list2}



    \textbf{Shenzhen Institutes of Advanced Technology (\href{http://english.siat.cas.cn/}{SIAT}),}   \\
    \textbf{Chinese Academy of Sciences (\href{http://english.cas.cn/}{CAS})}    \hfill \textbf{Shenzhen, China} \\

    \begin{list2}

    \item \textsl{Research project related to thesis}            \hfill \textbf{Sept. 2011 -- Jul. 2013}  \\
    Major works: 	Soft body deformation;
            		Mesh simplification;
            		Delaunay tetrahedralization;
            		Loop subdivision;
            		Displacement mapping using GLSL;
            		Finite Element Analysis;
            		CUDA implementation;
            		6 DOF haptic device.

    \item \textsl{Project granted by Shenzhen government}             \hfill \textbf{Aug. 2012 -- Feb. 2013}      \\
	Major works:	Volume/Surface rendering;
					CT reconstruction with CUDA implemented.
		       		%\item Project name: Virtual Robot-assisted Orthopedic Surgery Simulation System.
        			%\item My work includes: Volume/Surface rendering using ray casting algorithm.
        			% \item Using CUDA to accelerate 3D Cone-Beam CT reconstruction with simultaneous algebraic reconstruction technique (SART).
    
    \end{list2}



    \textbf{Central South University (\href{http://iecd.csu.edu.cn/en-US/Default.aspx}{CSU})}         \hfill \textbf{Changsha, China} \\

    \begin{list2}
	
	\item \textsl{Project leader in National University Student Innovation Program}.        \hfill \textbf{Sept. 2008 -- Dec. 2009}  \\
	Major works:	Calculation of fractal dimension;
					Visualization of fractal graphics;
					Simulation of force distribution in High Velocity Compaction. \\

    \end{list2}

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Honours \&\\Awards}

    2nd class prize in 4th \textsl{ACM CSU Collegiate Programming Contest}. ~ CSU, China    \hfill 2010      \\
    1st class prize in 3rd \textsl{CSU Mathematical Contest in Modeling}. ~ CSU, China      \hfill 2008      \\
    1st class prize in National High School Student Mathematics Competition. ~ China        \hfill 2005      \\


    %__________________________________________________________________________________________________________________
    % % Professional activities
    % \vspace{-5.0mm}
    % \line(1,0){440}
    % \vspace{-5.0mm}

    % \section{\mysidestyle Professional\\Activities}

    % \textbf{Membership}                                                 \\
    % ACM SIGGRAPH Asia 2011/2012/2013 (student) member                   \\


    %__________________________________________________________________________________________________________________
    % Computer Skills
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Useful \\Tools}

    \textbf{Programming Tools:} C/C++, CUDA, MATLAB, Python       \\
    \textbf{CG \& CV:} OpenGL, GLSL, Meshlab, OpenCV, Visual SFM, Kinect, Faceshift      \\
    \textbf{Others:} Mendeley, Git, \LaTeX  \\                                 

    %__________________________________________________________________________________________________________________
    % interesting
    %\section{\mysidestyle Other\\Interests}

    %\textbf{Chinese calligraphy:} I won lots of prizes in Chinese calligraphy competitions when I was a little boy.           \vspace{1mm}\\%
    %\textbf{Rubik's Cube:} I assisted a senior schoolmate to set up the Rubik¡¯s Cube Club in CSU.
    %Many schoolmates began to play it because of my promotion.                                                                                          %\vspace{1mm}\\%
    %\textbf{Badminton:} I was the president of badminton association in SIAT and organized badminton competition in fall, 2011.




%______________________________________________________________________________________________________________________
\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

