%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{Guo Yu - Page \thepage\ of 2}%当前页 of 总页数
\rfoot{}
\renewcommand{\headrulewidth}{0pt}%改为0pt即可去掉页眉下面的横线
\renewcommand{\footrulewidth}{0pt}%改为0pt即可去掉页脚上面的横线

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large GUO, Yu}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    50 Nanyang Drive, Research Techno Plaza             \hfill +65 8248 4728  \\
    Institute for Media Innovation                      \hfill \href{mailto:guoyu@ntu.edu.sg}{guoyu@ntu.edu.sg}  \\
    Nanyang Technological University                   \hfill \href{mailto:tflsguoyu@gmail.com}{tflsguoyu@gmail.com}\\
    Singapore, 637553               \hfill \href{http://www3.ntu.edu.sg/home/guoyu/}{http://www3.ntu.edu.sg/home/guoyu/} \\


    %__________________________________________________________________________________________________________________
    % Research Interests
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Current\\Position\&\\Interests}

    \textbf{Institute for Media Innovation (\href{http://imi.ntu.edu.sg/Pages/Home.aspx}{IMI}) @ \href{http://www.ntu.edu.sg/Pages/home.aspx}{NTU}}       \hfill \textbf{Singapore}  \\
    \textsl{Research Associate} \\
    Supervisor: \href{http://www.ntu.edu.sg/home/astjcham/}{Prof. Cham Tat-Jen} \textsl{(NTU)}  \\
    Collaborators: \href{https://graphics.ethz.ch/~plaffont/}{Dr. Pierre-Yves Laffont}\textsl{(ETH Z\"{u}rich)},
    \href{https://graphics.ethz.ch/~martint/}{Dr. Tobias Martin} \textsl{(ETH Z\"{u}rich)} \\
    Interests: Computer Graphics, Computer Vision, GPGPU \\

    %__________________________________________________________________________________________________________________
    % Education
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Education}

    \textbf{University of Chinese Academy of Sciences (\href{http://english.ucas.ac.cn/Pages/default.aspx}{UCAS})}    \hfill \textbf{Beijing \& Shenzhen, China}  \\
    \textsl{M.E. in Computer Science (GPA: 81/100)}                 \hfill \textbf{Sept. 2010 -- Jul. 2013} \\

    \begin{list2}
        \item Thesis: GPU-based Soft Body Deformation with Nonlinear Finite Element Method.
        \item Advisor: \href{http://www.cse.cuhk.edu.hk/~pheng/}{Prof. Heng Pheng-Ann} (\href{http://www.cuhk.edu.hk/english/index.html}{CUHK})
        \item Major courses: Combinatorial Mathematics; Matrix Analysis; Stochastic Process; Computer Aided Geometric Design; Computer Graphics; Computer Vision; Visualization.
    \end{list2}

    \textbf{Central South University (\href{http://iecd.csu.edu.cn/en-US/Default.aspx}{CSU})}      \hfill \textbf{Changsha, China} \\
    \textsl{B.S. in Mathematics and Applied Mathematics (GPA: 82/100)}                \hfill \textbf{Sept. 2006 -- Jul. 2010}  \\

    \begin{list2}
        \item Thesis: Forces Distribution with Fractal Theory in High Velocity Compaction Technology
        \item Advisor: Prof. Zheng Zhoushun (CSU)
        \item Major courses: Mathematical Analysis; Linear Algebra; Spatial and Analytical Geometry; Real Analysis \& Functional Analysis; Modern Algebra; Topology; Partial Differential Equation; Optimal Theory.
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Publications
    %\vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Publications}

    Derric Eng, Belle Yick, \textbf{Yu Guo}, Hong Xu, Miriam Reiner, Tat-Jen Cham, Annabel Chen.
    ``\textbf{Holistic and featural processing for 2D and 3D face recognition}".
    \textsl{The 11th Asia-Pacific Conference on Vision (APCV 2015)}, Singapore, July 10-12, 2015\\

    \vspace{-5mm}

    Ping Liu, Lin Shi, Defeng Wang, \textbf{Yu Guo}, Jianying Li, Jing Qin, Pheng-Ann Heng.
    ``\textbf{GPU Accelerated CBCT Reconstruction from Few Views with SART and TV Regularization}".
    \textsl{The Sixth International Workshop on High Performance Computing for Biomedical Image Analysis (HPC-MICCAI 2013)}, Nagoya, Japan, Sep.22-26, 2013\\

    \vspace{-5mm}

    Jiang Guo, Jun Cheng, Jianxin Pang, \textbf{Yu Guo}.
    ``\textbf{Real-time Hand Detection Based on Multi-stage HOG-SVM Classifier}".
    \textsl{2013 IEEE International Conference on Image Processing (ICIP 2013)}, Melbourne, Australia, Sep.15-18, 2013\\

    \vspace{-5mm}

    \textbf{Yu Guo}, Jianying Li, Ping Liu, Qiong Wang, Jing Qin.
    ``\textbf{A GPU-Accelerated Finite Element Solver for Simulation of Soft-Body Deformation}".
    \textsl{2013 IEEE International Conference on Information and Automation (ICIA 2013)}, Yinchuan, China, Aug.26-28, 2013\\

    \vspace{-5mm}

    \textbf{Yu Guo}, Jing Qin.
    ``\textbf{A Survey on Simulation of Soft Tissue Deformation in Virtual Surgery}"(In Chinese).
    \textsl{Journal of Integration Technology}, 2013\\

    \vspace{-5mm}

    \textbf{Yu Guo}.
    ``\textbf{Fall over or Sliding down?}"
    \textsl{ACM SIGGRAPH Asia 2012, Poster}, Singapore, Nov.28-Dec.1, 2012\\

    \vspace{-5mm}

    Jianying Li, \textbf{Yu Guo}, Heye Zhang, Yongming Xie.
    ``\textbf{A Master-Slave Robotic Simulator Based on GPUDirect}".
    \textsl{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2012)}, Vilamoura, Algarve, Portugal, Oct.7-12, 2012\\


    %________________________________________________________________________________________________________________
    % Professional Experience
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Research\\ Experiences}

    \textbf{Institute for Media Innovation (\href{http://imi.ntu.edu.sg/Pages/Home.aspx}{IMI}) @ \href{http://www.ntu.edu.sg/Pages/home.aspx}{NTU}}
    \hfill \textbf{Singapore} \\

    \vspace{-5mm}

    %\vspace{-2mm}%
    %\textsl{Project in BeingThere Centre, (\href{http://imi.ntu.edu.sg/BeingThereCentre/Pages/BTChome.aspx}{BTC-NTU} \& \href{http://beingthere.ethz.ch/}{BTC-ETH})}
    %\hfill \textbf{Aug. 2014 -- present}  \\\vspace{-4mm}%
    %\begin{list2}
     %   \item Project name: Glasses removal in video conference.
      %  \item My work includes:
       %     Flow estimation of image pairs (Optical Flow/Sift Flow);
        %    Face tracking and reconstruction by Kinect and Faceshift;
         %   Live streaming and color transfer using Blackmagic camera;
          %  Image Inpainting.
        %\item Collaborators: \href{https://graphics.ethz.ch/~martint/}{Dr. Tobias Martin} \textsl{(ETH Z\"{u}rich)},
    %                        \href{http://cs.brown.edu/~pylaffont/}{Dr. Pierre-Yves Laffont} \textsl{(ETH Z\"{u}rich)}
    %\end{list2}

    \textsl{Project in BeingThere Centre, (\href{http://imi.ntu.edu.sg/BeingThereCentre/Pages/BTChome.aspx}{BTC-NTU} \& \href{http://beingthere.ethz.ch/}{BTC-ETH})}
    \hfill  \textbf{Oct. 2013 -- May 2014}      \\

    \vspace{-3mm}

    \begin{list2}
        \item Physical-based video manipulating;
            Video segmentation (foreground subtraction);
            Multi-view 3D reconstruction (structure from motion);
            3D pose estimation.
        \item Collaborators: \href{https://graphics.ethz.ch/~jebazin/}{Dr. Jean-Charles Bazin} \textsl{(Disney Z\"{u}rich)},
                            \href{https://graphics.ethz.ch/~martint/}{Dr. Tobias Martin} \textsl{(ETH Z\"{u}rich)},
                            \href{https://graphics.ethz.ch/~ckuster/}{Dr. Claudia Kuster} \textsl{(ETH Z\"{u}rich)}
    \end{list2}

    \textsl{Project in BeingThere Centre, (\href{http://imi.ntu.edu.sg/BeingThereCentre/Pages/BTChome.aspx}{BTC-NTU} \& \href{http://www.hss.ntu.edu.sg/Pages/Home.aspx}{HSS-NTU})}
    \hfill  \textbf{Dec. 2013 -- Dec. 2014}      \\

    \vspace{-3mm}

    \begin{list2}
        \item 2D and stereo face rendering
        \item Collaborators: \href{http://edu.technion.ac.il/haptech/group/miriam_home.html}{Prof. Miriam Reiner} \textsl{(Technion)},
                            \href{http://www.hss.ntu.edu.sg/Programmes/psychology/people/Pages/BelleYick.aspx}{Dr. Belle Yee Ying Yick} \textsl{(NTU)}
    \end{list2}



    \textbf{Shenzhen Institutes of Advanced Technology (\href{http://english.siat.cas.cn/}{SIAT}),}   \\
    \textbf{Chinese Academy of Sciences (\href{http://english.cas.cn/}{CAS})}    \hfill \textbf{Shenzhen, China} \\

    \vspace{-5mm}

    \textsl{Research project related to thesis}            \hfill \textbf{Sept. 2011 -- Jul. 2013}  \\

    \vspace{-3mm}

    \begin{list2}
        \item Soft body deformation;
            Mesh simplification;
            Delaunay tetrahedralization;
            Loop subdivision;
            Displacement mapping using GLSL;
            Finite Element Analysis;
            CUDA implementation;
            6 DOF haptic device.
    \end{list2}

    \textsl{Project granted by Shenzhen government}             \hfill \textbf{Aug. 2012 -- Feb. 2013}      \\

    \vspace{-3mm}

    \begin{list2}
        %\item Project name: Virtual Robot-assisted Orthopedic Surgery Simulation System.
        %\item My work includes: Volume/Surface rendering using ray casting algorithm.
        \item Using CUDA to accelerate 3D Cone-Beam CT reconstruction with simultaneous algebraic reconstruction technique (SART).
    \end{list2}



    \textbf{Central South University (\href{http://iecd.csu.edu.cn/en-US/Default.aspx}{CSU})}         \hfill \textbf{Changsha, China} \\

    \vspace{-5mm}

    \textsl{Project leader in National University Student Innovation Program}.        \hfill \textbf{Sept. 2008 -- Dec. 2009}  \\

    \vspace{-3mm}

    \begin{list2}
        \item Calculation of fractal dimension, visualization of fractal graphics,
        and simulation of force distribution in High Velocity Compaction.
    \end{list2}


    %__________________________________________________________________________________________________________________
    % Honours and Awards
    %\vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Honours \&\\Awards}

    2nd class prize in 4th \textsl{ACM CSU Collegiate Programming Contest}. ~ CSU, China    \hfill 2010      \\
    1st class prize in 3rd \textsl{CSU Mathematical Contest in Modeling}. ~ CSU, China      \hfill 2008      \\
    1st class prize in National High School Student Mathematics Competition. ~ China        \hfill 2005      \\


    %__________________________________________________________________________________________________________________
    % Professional activities
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Professional\\Activities}

    \textbf{Membership}                                                 \\
    ACM SIGGRAPH Asia 2011/2012/2013 (student) member                   \\


    %__________________________________________________________________________________________________________________
    % Computer Skills
    \vspace{-5.0mm}
    \line(1,0){440}
    \vspace{-5.0mm}

    \section{\mysidestyle Skills}

    \textbf{Programming Tools:}  Visual Studio C/C++, CUDA, MATLAB       \\
    \textbf{Computer Graphics:} OpenGL (glut/glew), GLSL, Meshlab        \\
    \textbf{Computer Vision:} OpenCV, visual SFM, Kinect, Faceshift      \\
    \textbf{Others:} MS Office, \LaTeX                                   \\

    %__________________________________________________________________________________________________________________
    % interesting
    %\section{\mysidestyle Other\\Interests}

    %\textbf{Chinese calligraphy:} I won lots of prizes in Chinese calligraphy competitions when I was a little boy.           \vspace{1mm}\\%
    %\textbf{Rubik's Cube:} I assisted a senior schoolmate to set up the Rubik’s Cube Club in CSU.
    %Many schoolmates began to play it because of my promotion.                                                                                          %\vspace{1mm}\\%
    %\textbf{Badminton:} I was the president of badminton association in SIAT and organized badminton competition in fall, 2011.




%______________________________________________________________________________________________________________________
\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

